---
title: "Final Project: Exploratory Data Analysis"
authors: "Yiyang Fan, Rindha Sudhini, Julia Straight, Wenqiong Hu, Zihan Zhang, Joey Burroughs"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r, message=FALSE, echo=FALSE}
library(tidyverse)
library(readr)
library(forcats)
library(ggplot2)
```

```{r, message=FALSE, echo=FALSE, results='hide'}
setwd=("/Users/fanyiyang/Desktop/UNC/Course/Stor320/Final\ Project ")
movie=read_csv("/Users/fanyiyang/Desktop/UNC/Course/Stor320/Final\ Project/movie.csv")
Action=str_detect(movie$Genre,"Action")
Action
movie1=cbind(movie,Action)
str(movie)
names(movie)
movie2=movie%>%
  rename(domestic_sales=names(movie)[6],
         international_sales=names(movie)[7],
         total_sales=names(movie)[8],
         date=names(movie)[5])%>%
  separate(date,into=c("date","year"),sep=",")%>%
  mutate(year=as.numeric(year))
str(movie2)
movie2%>%
  group_by(Distributor)%>%
  summarize(mean=mean(total_sales),
            sd=sd(total_sales))%>%
  arrange(mean)
write_csv(movie2,"new_movie.csv")
```

```{r, message=FALSE, echo=FALSE, results='hide'}
movie3=movie2%>%
  mutate(`Movie Runtime`=str_replace(`Movie Runtime`,"hr",""),
         `Movie Runtime`=str_replace(`Movie Runtime`,"min",""),
         `Movie Runtime`=str_replace_all(`Movie Runtime`," ",""),
         time=as.numeric(`Movie Runtime`),
         minutes=ifelse(time>=100,time%/%100*60+time%%100,ifelse(time>=10,time%/%10*60+time%%10,time*60)))%>%
  dplyr::select(-`Movie Runtime`,-time)
setwd=("/Users/juliastraight/Desktop//stor 320/Final\ Project")
write_csv(movie3,"New_MOVIE.csv")
```

```{r, message=FALSE, echo=FALSE, results='hide'}
movie4=movie3%>%
  mutate(Action=ifelse(str_detect(Genre,"Action"),1,0),
         Adventure=ifelse(str_detect(Genre,"Adventure"),1,0),
         `Sci-Fi`=ifelse(str_detect(Genre,"Sci-Fi"),1,0),
         Romance=ifelse(str_detect(Genre,"Romance"),1,0),
         Fantasy=ifelse(str_detect(Genre,"Fantasy"),1,0),
         Animation=ifelse(str_detect(Genre,"Animation"),1,0),
         Family=ifelse(str_detect(Genre,"Family"),1,0),
         Comedy=ifelse(str_detect(Genre,"Comedy"),1,0),
         Musical=ifelse(str_detect(Genre,"Musical"),1,0),
         Crime=ifelse(str_detect(Genre,"Crime"),1,0),
         Drama=ifelse(str_detect(Genre,"Drama"),1,0),
         Thriller=ifelse(str_detect(Genre,"Thriller"),1,0),
         Mystery=ifelse(str_detect(Genre,"Mystery"),1,0),
         Biography=ifelse(str_detect(Genre,"Biography"),1,0),
         Sport=ifelse(str_detect(Genre,"Sport"),1,0),
         Horror=ifelse(str_detect(Genre,"Horror"),1,0),
         total=Action+Adventure+`Sci-Fi`+Romance+Fantasy+Animation+Family+Comedy+Musical+Crime+Drama+Thriller+Mystery+Biography+Sport+Horror)%>%
  separate(Title,into=c("title","year in parenthesis"),sep=-6)
write_csv(movie4,"FINAL_MOVIE.csv")
```


**Question 1:** What periods were different popular distributors the most prolific?
```{r, message=FALSE, echo=FALSE}
movie4=read_csv("FINAL_MOVIE.csv")
movie4%>%
group_by(Distributor)%>%
count()%>%
ggplot()+
geom_bar(stat="identity",aes(x=n,y=Distributor)) + ggtitle("Popularity of Distrubutors")+ xlab("Count")

movie4%>%
group_by(Distributor)%>%
mutate(n=n())%>%
filter(!is.na(year),n>50)%>%
group_by(year,Distributor)%>%
count()%>%
ggplot(aes(x=year,y=n))+
geom_point()+
geom_line()+
facet_wrap(~Distributor,nrow=4) + ggtitle("Popularity of Distributors") + xlab("Year") + ylab("Movies Released")
```



**Question 1 Follow-up:** Is there an indication of covariance between the most popular distributors? How do the most popular distributors' movie releases line up with each other?
```{r, message=FALSE, echo=FALSE, warning=FALSE}
movie4%>%
group_by(Distributor)%>%
mutate(n=n())%>%
filter(n>110)%>%
ungroup()%>%
filter(!is.na(year))%>%
ggplot(aes(x=year,color=Distributor))+
geom_freqpoly()+
xlab("Year of Release")+
ylab("Number of movies") + ggtitle("Comparing Distributor Popularity")
```


**Question 2:** What is the relationship between the distributors and the percent of sales?
```{r, message=FALSE, echo=FALSE}
movie4%>%
group_by(Distributor)%>%
count()%>%
ggplot()+
geom_bar(stat="identity",aes(x=n,y=Distributor)) + ggtitle("Popularity of Distrubutors")+ xlab("Count")

movie3%>%
  mutate(percent=domestic_sales/total_sales)%>%
  group_by(Distributor)%>%
  mutate(n=n())%>%
  filter(n>5)%>%
  summarize(mean=mean(percent,na.rm=T))%>%
  ggplot(aes(y=fct_reorder(Distributor,mean),x=mean))+
  geom_bar(stat="identity")+ ggtitle("Sales by Distributor") + xlab("Proportion of Domestic Sales") + ylab("Distributor")
```


**Question 3:** Of the overall most popular genres, how have trends in which genre is most popular shifted over the years?
```{r, message=FALSE, echo=FALSE, warning=FALSE}
sum=rep(0,16)
for (i in c(14:29)){
  sum[i-12]=sum(movie4[[i]])
}
names(sum)=names(movie4)[14:29]
barplot(sum, las=2, main="Popularity of Genres", ylab = "Movie Count")
colors=c("action"="red","adventure"="blue","comedy"="red","drama"="grey")
plot=ggplot() + ggtitle("Popularity by Genre") + xlab("Year") + ylab("Movie Count")
plot=plot+geom_freqpoly(filter(movie4,Action==1),mapping=aes(x=year,color="action"),size=1.5)
plot=plot+geom_freqpoly(filter(movie4,Adventure==1),mapping=aes(x=year,color="adventure"),size=1.5)
plot=plot+geom_freqpoly(filter(movie4,Comedy==1),mapping=aes(x=year,color="comedy"),size=1.5)
plot=plot+geom_freqpoly(filter(movie4,Drama==1),mapping=aes(x=year,color="drama"),size=1.5)
plot
```

**Question 4:** How do international and domestic sales respond to different runtime?
```{r, message=FALSE, echo=FALSE}
minute_sale=movie4%>%
  group_by(minutes)%>%
  summarize(domestic_mean=mean(domestic_sales,na.rm=T),
         international_mean=mean(international_sales,na.rm=T))
plot=ggplot() + ggtitle("Domestic(Red) vs International(Blue) Sales") + xlab("Movie Length in Minutes") + ylab("Sales")
domestic=geom_line(minute_sale,mapping=aes(x=minutes,y=domestic_mean),col="red")
international=geom_line(minute_sale,mapping=aes(x=minutes,y=international_mean),col="blue")
plot+domestic+international

# need legend
```



**Question 5:** Is there a difference in the international and domestic preference of genres?
```{r, message=FALSE, echo=FALSE}
ratio=rep(0,16)
for (i in c(14:29)){
  part=filter(movie4,movie4[i]==1)
  ratio[i-13]=mean(part[["domestic_sales"]]/part[["total_sales"]])
}
names(ratio)=names(movie4)[14:29]
data.frame(as.list(ratio))%>%
  gather(Action:Horror,key=genre,value=rate)%>%
  ggplot()+ ggtitle("Domestic Proportion of Total Sales by Genre") + xlab("Proportion of Total Sales") + ylab("Genre") + 
  geom_bar(stat="identity",aes(y=fct_reorder(genre,ratio),x=rate))
```
Generating confidence intervals
```{r}
movie5=movie4%>%
  mutate(prop=domestic_sales/total_sales)
MEAN_PROP=mean(movie5$prop,na.rm=T)
mean=rep(0,16)
se=rep(0,16)
for (i in c(14:29)){
  part=filter(movie5,movie5[i]==1)
  mean[i-13]=mean(part$prop,na.rm=T)
  se[i-13]=sd(part$prop,na.rm=T)/sqrt(length(part$prop))
}
left_bound=mean-2*se
right_bound=mean+2*se
as.data.frame(cbind(names(movie4)[14:29],mean,se,left_bound,right_bound))%>%
  rename("genre"=`V1`)%>%
  mutate(mean=as.numeric(mean),
         left_bound=as.numeric(left_bound),
         right_bound=as.numeric(right_bound),
         spread=ifelse(left_bound>MEAN_PROP,1,ifelse(right_bound<MEAN_PROP,-1,0)))%>%
  ggplot()+
  geom_errorbar(aes(y=genre,xmin=left_bound,xmax=right_bound,col=as.factor(spread)))+
  geom_vline(xintercept=MEAN_PROP,linetype = "longdash",col="red")+
  geom_point(aes(x=mean,y=genre),fill="white",size=4,shape=21)+
  xlab("domestic sales / total sales")
```
As action is significantly below average, what kind of combination will make action less popular domestically compared with internationally?
```{r}
genre_covariance=matrix(NA,16,16)
colnames(genre_covariance)=names(movie4)[14:29]
rownames(genre_covariance)=names(movie4)[14:29]
for (i in c(14:29)){
  genre_specific=filter(movie5,movie5[i]==1)
  mean=rep(0,16)
  se=rep(0,16)
  for (j in c(14:29)){
    part=filter(genre_specific,genre_specific[j]==1)
    mean[j-13]=mean(part$prop,na.rm=T)
    se[j-13]=sd(part$prop,na.rm=T)/sqrt(length(part$prop))
  }
  left_bound=mean-2*se
  right_bound=mean+2*se
  data=as.data.frame(cbind(names(movie4)[14:29],mean,se,left_bound,right_bound))%>%
      rename("genre"=`V1`)%>%
      mutate(mean=as.numeric(mean),
            left_bound=as.numeric(left_bound),
            right_bound=as.numeric(right_bound),
            spread=ifelse(left_bound>MEAN_PROP,1,ifelse(right_bound<MEAN_PROP,-1,0)))
  for (k in c(1:16)){
    genre_covariance[i-13,k]=data$spread[k]
  }
}
genre_covariance
```
```{r}
as.data.frame(genre_covariance)%>%
  mutate(genre=row.names(.))%>%
  gather(Action:Horror,key="genre2",value="spread")%>%
  ggplot()+
  geom_tile(aes(x=genre2,y=genre,fill=factor(spread)),col="black")+
  theme(axis.text.x = element_text(angle = 90))+
  scale_fill_manual(values = c("deepskyblue","lightblue","blue"))+
  geom_abline(a=0,b=1)
```



**Question 6:** How does run time affect the popularity of movie?
```{r, message=FALSE, echo=FALSE}
movie3%>%
  group_by(minutes)%>%
  summarize(mean=mean(total_sales))%>%
  ggplot(aes(x=minutes,y=mean)) + ylab("Sales") + geom_point() + ggtitle("Run time and Popularity by Sales") + xlab("Run time in minutes")
movie3%>%
  ggplot(aes(x=cut_width(minutes,10),y=total_sales))+
  geom_boxplot()+
  coord_flip()+
  xlab("Movie length in minutes")+
  ylab("Movie total sales")+
  ggtitle("The relationship between run time and movie total sales")
```

**Question 6 Follow-up:** Does the relationship between run time and sales continue within different production companies?

**Question 7:** What percentage do domestic sales contain of the total world sales?
```{r, message=FALSE, echo=FALSE}
library(tidyverse) #Loads the tidyverse package for ggplot
library(pscl) #Loads the pscl package for the dataset
library(gridExtra) #Allows us to combine ggplots into a nice layout
total=movie4%>%
  mutate(ratio=domestic_sales/total_sales)%>%
  ggplot(aes(x=cut_width(year,10),y=ratio))+
  geom_boxplot() + ggtitle("Total Domestic Sales") + xlab("Year") + ylab("Proportion of Global Sales")
total
```


**Question 7 Follow-up:** How does genre popularity differ between international and domestic audiences? Does a similar trend follow for popular genres such as Action and Adventure?
```{r, message=FALSE, echo=FALSE}
# barplot(sum, las=2, main="Popularity of Genres", ylab = "Movie Count")

action=movie4%>%
  mutate(ratio=domestic_sales/total_sales)%>%
  filter(Action==1)%>%
  ggplot(aes(x=cut_width(year,10),y=ratio))+
  geom_boxplot()+
  ggtitle("Domestic Action Sales")+ xlab("Year") + ylab("Proportion of Global Sales") + scale_x_discrete(guide = guide_axis(angle = 45))
adventure=movie4%>%
  mutate(ratio=domestic_sales/total_sales)%>%
  filter(Adventure==1)%>%
  ggplot(aes(x=cut_width(year,10),y=ratio))+
  geom_boxplot()+
  ggtitle("Domestic Adventure Sales")+ xlab("Year") + ylab("Proportion of Global Sales") + scale_x_discrete(guide = guide_axis(angle = 45))
LAYOUT=matrix(c(1,2,1,3),ncol=2)
grid.arrange(total,action,adventure,layout_matrix=LAYOUT)
```


**Question 8:** Is there a correlation between movie name length and sales?

```{r, message=FALSE, echo=FALSE}
movie4%>%
  mutate(name_length=nchar(title))%>%
  group_by(name_length)%>%
  mutate(mean=mean(total_sales))%>%
  ggplot(aes(x=name_length,y=mean))+
  geom_point() + xlab("Characters in Movie Title") + ylab("Sales") + ggtitle("Title Length and Sales")
```


**Question 8 Follow-up:** How many range of characters should be in a movie name to maximize sales?


**Question 9:** How does grouping/trends within the most popular distributors work? 
```{r, message=FALSE, echo=FALSE, warning=FALSE}
movie4%>%
group_by(Distributor)%>%
count()%>%
ggplot()+
geom_bar(stat="identity",aes(x=n,y=Distributor)) + ggtitle("Popularity of Distrubutors")+ xlab("Count")

library(gridExtra)
Disney=rep(0,16)
for (i in c(13:28)){
  Disney[i-12]=dim(filter(movie4,movie4[i]==1,Distributor=="Walt Disney Studios Motion Pictures"))[1]
}
names(Disney)=names(movie4)[13:28]
disney=as.tibble(cbind(Disney,names(movie4)[13:28]))%>%
  rename(count=Disney,
         genre=`V2`)%>%
  mutate(count=as.numeric(count),
         perc=count/sum(count),
         perc=round(perc,2),)%>%
  arrange(perc)%>%
  ggplot(aes(perc,fct_reorder(genre,perc))) + ggtitle("Disney") + xlab("Percent of Sales") + ylab("Genre") +
  geom_bar(stat="identity")
Warner=rep(0,16)
for (i in c(13:28)){
  Warner[i-12]=dim(filter(movie4,movie4[i]==1,Distributor=="Warner Bros."))[1]
}
names(Warner)=names(movie4)[13:28]
warner=as.tibble(cbind(Warner,names(movie4)[13:28]))%>%
  rename(count=Warner,
         genre=`V2`)%>%
  mutate(count=as.numeric(count),
         perc=count/sum(count),
         perc=round(perc,2),)%>%
  arrange(perc)%>%
  ggplot(aes(perc,fct_reorder(genre,perc))) + 
  geom_bar(stat="identity") + ggtitle("Warner Bros") + xlab("Percent of Sales") + ylab("Genre") 
Sony=rep(0,16)
for (i in c(13:28)){
  Sony[i-12]=dim(filter(movie4,movie4[i]==1,Distributor=="Sony Pictures Entertainment (SPE)"))[1]
}
names(Sony)=names(movie4)[13:28]
sony=as.tibble(cbind(Sony,names(movie4)[13:28]))%>%
  rename(count=Sony,
         genre=`V2`)%>%
  mutate(count=as.numeric(count),
         perc=count/sum(count),
         perc=round(perc,2),)%>%
  arrange(perc)%>%
  ggplot(aes(perc,fct_reorder(genre,perc))) + ggtitle("Sony") + xlab("Percent of Sales") + ylab("Genre") +
  geom_bar(stat="identity")
LAYOUT=matrix(c(1,2,1,3),ncol=2)
grid.arrange(sony,disney,warner,layout_matrix=LAYOUT)
```

**Question 10:** Do release dates have a seasonal affect on sales?
```{r, message=FALSE, echo=FALSE}
date=movie4%>%
  filter(!is.na(date))%>%
  separate(date,into=c("month","day"),sep=" ")%>% #only 800 observations 
  mutate(month=factor(month,unique(month)),
         month=fct_collapse(month,
        Winter=c("December", "January","February"),
        Spring=c("March", "April","May"),
        Summer=c("June", "July","August"),
        Autumn=c("September", "October","November")))
  
date%>%
  ggplot()+
  geom_boxplot(aes(x=month,y=total_sales)) + ggtitle("Total Sales based on Season of Release") + xlab("Season") + ylab("Total Sales")

```

**Question 11:** Does the release year impact the run time? Is there an increase/decrease?
```{r, message=FALSE, echo=FALSE}
movie3%>%
  filter(!is.na(year))%>%
  group_by(year)%>%
  summarize(mean=mean(minutes))%>%
  ggplot(aes(x=year,y=mean))+
  geom_point() + ggtitle("Release Year and Run Time") + xlab("Year") + ylab("Run Time in Minutes")
```


**Question 12:** Do genres tend to stick to a certain range of run-time?
```{r, message=FALSE, echo=FALSE}
mean=rep(0,16)
sd=rep(0,16)
first_quantile=rep(0,16)
third_quantile=rep(0,16)
for (i in c(13:28)){
part=filter(movie4,movie4[i]==1)
mean[i-12]=mean(part$minutes)
sd[i-12]=sd(part$minutes)
first_quantile[i-12]=quantile(part$minutes,0.25)
third_quantile[i-12]=quantile(part$minutes,0.75)
}
as.data.frame(cbind(names(movie4)[13:28],mean,sd,first_quantile,third_quantile))%>%
mutate(mean=as.numeric(mean),
sd=as.numeric(sd),
first_quantile=as.numeric(first_quantile),
third_quantile=as.numeric(third_quantile))%>%
rename(genre=`V1`)%>%
ggplot()+
geom_errorbar(aes(y=genre,xmin=first_quantile,xmax=third_quantile))+
geom_point(aes(x=mean,y=genre),fill="white",size=4,shape=21)
```
Webscrap the rating
```{r}
library(rvest)    
rating=read_csv("https://raw.githubusercontent.com/dineshsonachalam/IMDB_5000_Movies_Statistics_Report-/master/movie_metadata.csv")%>%
  separate(movie_title,into=c("title","no"),sep=-1)%>%
  dplyr::select(title,budget,imdb_score)
movie5=movie4%>%
  separate(title,into=c("title","no"),sep=-1)

movie6=movie4%>%
  left_join(rating,by="title")%>%
  filter(!is.na(imdb_score))
```

Generating predictive models about the domestic sales
```{r}
library(purrr)
library(modelr)
movie7=movie6%>%
  mutate(name_length=nchar(title))%>%
  filter(!is.na(date))%>%
  separate(date,into=c("month","day"),sep=" ")%>% #only 800 observations 
  mutate(month=factor(month,unique(month)),
         month=fct_collapse(month,
        Winter=c("December", "January","February"),
        Spring=c("March", "April","May"),
        Summer=c("June", "July","August"),
        Autumn=c("September", "October","November")),
        log_domestic=log(domestic_sales),
        log_international=log(international_sales))%>%
  dplyr::select(Action:Horror,month,year,minutes,budget,imdb_score,log_domestic,log_international)
```

First model: linear
```{r}
data=crossv_kfold(na.omit(movie7),k=10)
model.func=function(data){
  mod=lm(log_domestic~Action:Horror+month+year+minutes+budget+imdb_score,data=data) # log of domestic
  return(mod)
}
data2=data%>%
  mutate(model=map(train,model.func))
head(data2)
```

```{r}
library(broom)
data2.predict=data2%>%
  mutate(predict=map2(.x=test,.y=model,~augment(.y,newdata=.x)))%>%
  dplyr::select(predict)%>%
  unnest()
RMSE.func=function(actual,predict){
  SSE=sum((actual-predict)^2)
  return(sqrt(SSE/length(actual)))
}
INITIAL_RMSE=RMSE.func(data2.predict$log_domestic,data2.predict$.fitted)
```

```{r}
ggplot(data=data2.predict)+
  geom_point(aes(x=.fitted,y=log_domestic))+
  geom_abline(col="red")
```

Second Model: manually choose variables
```{r}
lm.fit=lm(log_domestic~.,movie7)
coeff=tidy(lm.fit)%>%
  filter(p.value<0.05)%>%
  dplyr::select(term,estimate)
m=model.matrix(log_domestic~.,na.omit(movie7))
model=na.omit(movie7)%>%
  mutate(predict=m[,coeff[[1]]]%*%coeff[[2]])
EIGHT_VARIABLE_RMSE=RMSE.func(model$log_domestic,model$predict)
model%>%
  ggplot()+
  geom_point(aes(x=predict,y=log_domestic))+
  geom_abline(col="red")
```


Third Model: best subset
```{r}
library(leaps)
regfit.full=regsubsets(log_domestic~.,data=movie7,nvmax=22)
summary1=summary(regfit.full)
par(mfrow=c(2,2))
plot(summary1$rss,xlab="Number of Variables",ylab="RSS",type="l") #type="l" connects the plotted points with lines
plot(summary1$adjr2,xlab="Number of variables",ylab="Adjusted R^2",type="l")
# I believe 14 variable-model is good enough
coef=coef(regfit.full,14)
coef
m=model.matrix(log_domestic~.,na.omit(movie7))
model2=na.omit(movie7)%>%
  mutate(predict=m[,names(coef)]%*%coef)
best_subset_RMSE=RMSE.func(model2$log_domestic,model2$predict)
```

Fourth Model: Best subset with cross validation
```{r}
predict.regsubsets=function(object,newdata,id,...){
  form=as.formula(object$call[[2]])
  mat=model.matrix(form,newdata)
  coefi=coef(object,id=id)
  yvars=mat[,names(coefi)]
  return(yvars%*%coefi)
}
set.seed(2)
fold=sample(1:10,nrow(na.omit(movie7)),rep=T)
cv.sse=matrix(NA,10,22,dimnames=list(NULL,paste(1:22)))
for (i in 1:10){
  regfit=regsubsets(log_domestic~.,na.omit(movie7),nvmax=22,subset=(fold!=i))
  for (j in 1:22){
    predict=predict.regsubsets(regfit,na.omit(movie7)[fold==i,],id=j)
    cv.sse[i,j]=mean((na.omit(movie7)$log_domestic[fold==i]-predict)^2)
  }
}
mean.cv.sse=apply(cv.sse,2,mean,drop=T)
mean.cv.sse
plot(mean.cv.sse)
CV.SUBSET.RMSE=sqrt(mean.cv.sse[4])
```

Fifth Model: Lasso
```{r}
library(glmnet)
x=model.matrix(log_domestic~.,select(na.omit(movie7),-log_international))[,-1]
y=na.omit(movie7)$log_domestic
lambda_grid=10^seq(10,-2,length=100)

test=(-train)
lasso.fit=glmnet(x,y,alpha=1,lambda=lambda_grid)
plot(lasso.fit)
cv.out=cv.glmnet(x,y,alpha=1)
plot(cv.out)
bestLambda=cv.out$lambda.1se
LASSO_RMSE=min(cv.out$cvm)
bestLambda
best.lasso.fit=glmnet(x,y,alpha=1,lambda=bestLambda)
na.omit(movie7)%>%
  mutate(predict=predict(best.lasso.fit,newx=x))%>%
  ggplot()+
  geom_point(aes(x=predict,y=log_domestic))+
  geom_abline(col="red")
lasso_coef=coef(best.lasso.fit)
lasso_coef=lasso_coef[lasso_coef[,1]!=0,]
lasso_coef
```

Sixth model: Lasso with interaction
```{r}
library(glmnet)
set.seed(20)
x=model.matrix(log_domestic~.*.,select(na.omit(movie7),-log_international))[,-1]
y=na.omit(movie7)$log_domestic
lambda_grid=10^seq(10,-2,length=100)

test=(-train)
lasso.fit=glmnet(x,y,alpha=1,lambda=lambda_grid)
plot(lasso.fit)
cv.out=cv.glmnet(x,y,alpha=1)
plot(cv.out)
bestLambda=cv.out$lambda.1se
LASSO_RMSE=min(cv.out$cvm)
bestLambda
best.lasso.fit=glmnet(x,y,alpha=1,lambda=bestLambda)
predict(best.lasso.fit,newx=x)
lasso_coef=coef(best.lasso.fit)
lasso_interaction_coef=lasso_coef[lasso_coef[,1]!=0,]
lasso_interaction_coef
```

compare models
```{r}
domestic_models=tribble(
  ~model, ~RMSE,  ~variables,
  "lm", INITIAL_RMSE,  23,
  "lm2", EIGHT_VARIABLE_RMSE,  8,
  "Best Subset", best_subset_RMSE, 14,
  "CV Best Subset", CV.SUBSET.RMSE, 4,
  "Lasso", LASSO_RMSE , 11
  )
domestic_models
```

Change dataset to predict international sale
```{r}
movie8=movie6%>%
  mutate(name_length=nchar(title))%>%
  filter(!is.na(date))%>%
  separate(date,into=c("month","day"),sep=" ")%>% #only 800 observations 
  mutate(month=factor(month,unique(month)),
         month=fct_collapse(month,
        Winter=c("December", "January","February"),
        Spring=c("March", "April","May"),
        Summer=c("June", "July","August"),
        Autumn=c("September", "October","November")),
        log_international=log(international_sales))%>%
  dplyr::select(Action:Horror,month,year,minutes,budget,imdb_score,log_international)
```

CV subset for international
```{r}
fold=sample(1:10,nrow(na.omit(movie7)),rep=T)
cv.sse=matrix(NA,10,22,dimnames=list(NULL,paste(1:22)))
for (i in 1:10){
  regfit=regsubsets(log_domestic~.,na.omit(movie7),nvmax=22,subset=(fold!=i))
  for (j in 1:22){
    predict=predict.regsubsets(regfit,na.omit(movie7)[fold==i,],id=j)
    cv.sse[i,j]=mean((na.omit(movie7)$log_domestic[fold==i]-predict)^2)
  }
}
mean.cv.sse=apply(cv.sse,2,mean,drop=T)
mean.cv.sse
plot(mean.cv.sse)
```

Lasso for international
```{r}
set.seed(20)
x=model.matrix(log_international~.,na.omit(movie8))
y=na.omit(movie8)$log_international
lambda_grid=10^seq(10,-2,length=100)
train=sample(1:nrow(x),nrow(x)/2)
test=(-train)
lasso.fit=glmnet(x[train,],y[train],alpha=1,lambda=lambda_grid)
plot(lasso.fit)
cv.out=cv.glmnet(x[train,],y[train],alpha=1)
plot(cv.out)
bestLambda=cv.out$lambda.min
LASSO_RMSE=min(cv.out$cvm)
bestLambda
best.lasso.fit=glmnet(x[train,],y[train],alpha=1,lambda=bestLambda)
coef(best.lasso.fit) #interpret the model
```
```{r}
as.data.frame(genre_covariance)%>%
  mutate(genre=row.names(.))%>%
  gather(Action:Horror,key="genre2",value="spread")%>%
  ggplot()+
  geom_tile(aes(x=genre2,y=genre,fill=factor(spread)),col="black")+
  theme(axis.text.x = element_text(angle = 90))+
  scale_fill_manual(values = c("deepskyblue","lightblue","blue"),
                    name = "spread", labels = c("less than average", "contains average", "more than average","no observation"))+
  geom_abline(a=0,b=1)
```

**Reflection Paragraphs:**
In our initial questions, there were two types of questions we were exploring: relationships between different groups in a variable and where we wanted to see if a relationship existed at all. Questions that fell in the first category included comparing the popularity of different distributors over time, how international and domestic sales were split, and audience preference of genres. These questions allowed us to see differences within a variable (distributors, genre) and compare the responses of these subgroups to each other. Interestingly enough, the second category of our questions revealed that moderate to strong relationships existed between more variables than originally thought. This included positive correlations between the characters in a movie name and run-time with the number of sales, which we did not expect. 

While answering the initial questions and their resulting graphs, we created follow-up questions that dived deeper. An example of this is our first follow-up question which asked about covariance between different distributors. We wanted to know if the popularity of distributors depended on other distributors at the time, and from our graph, there was an indication that covariance did exist as the increase in sales for one distributor was often followed by the decrease in sales of other distributors. Another one of our follow-up questions aimed to understand how genre preference varied between international and domestic audiences. The data revealed that each audience did have a preference towards a specific genre, and it also showed us the benefit of asking questions that explored specific details, rather than just establishing a correlation. 

